Measurement Bias from Address Aliasing

### 2016-05-26 presentation.tex
Add slide with results from other architectures

\begin{table}
  \caption{Events with significant correlation to cycle count.\label{tab:loopcorrelation}}
  \pgfplotstabletypeset[
    int detect, % Output whole numbers for counter values
    col sep=comma,
    highlightrow={1},
    columns={Performance counter, Median, [index]3, [index]4},
    column type=r,
    font=\footnotesize,
    columns/Performance counter/.style={
      string type, 
      column type=l,
      column type/.add={|}{},
      postproc cell content/.append code={
        \pgfkeysalso{@cell content=\perfctr{##1}}
      }
    },
    every head row/.style={
      output empty row,
      before row={\hline
        Performance counter & Median & Spike 1 & Spike 2 \\
      },
      after row=\hline\hline
    },
    every last row/.style={after row=\hline},
    every last column/.style={column type/.add={}{|}}
  ]{bin/microkernel-comparison-haswell.csv}
\end{table}
\end{frame}

@@

>>>>

\begin{table}
  \caption{Events with significant correlation to cycle count.\label{tab:loopcorrelation}}
  \pgfplotstabletypeset[
    int detect, % Output whole numbers for counter values
    col sep=comma,
    highlightrow={1},
    columns={Performance counter, Median, [index]3, [index]4},
    column type=r,
    font=\footnotesize,
    columns/Performance counter/.style={
      string type, 
      column type=l,
      column type/.add={|}{},
      postproc cell content/.append code={
        \pgfkeysalso{@cell content=\perfctr{##1}}
      }
    },
    every head row/.style={
      output empty row,
      before row={\hline
        Performance counter & Median & Spike 1 & Spike 2 \\
      },
      after row=\hline\hline
    },
    every last row/.style={after row=\hline},
    every last column/.style={column type/.add={}{|}}
  ]{bin/microkernel-comparison-haswell.csv}
\end{table}

@@

\begin{frame}[fragile]
  \pgfplotstableread{bin/microkernel-core.dat}{\tblmicrokernelcore}
  \pgfplotstableread{bin/microkernel-nehalem.dat}{\tblmicrokernelnehalem}
  \pgfplotstableread{bin/microkernel-ivybridge.dat}{\tblmicrokernelivybridge}
  \frametitle{Other architectures}
  \begin{columns}[T] % align columns
    \begin{column}{.50\textwidth}
      \begin{tikzpicture}
        \begin{axis}[
            title = Core,
            width = \textwidth/0.85,
            height = 4.0cm,
            font = \footnotesize,
            domain = 0:4096,
            xtick = {0,1024,...,4096},
            xmin = 0,
            xmax = 4096,
            cycle list name = exotic
          ]
          \addplot[ycomb] table[x expr = \thisrowno{0}*16, y = cycles:u] \tblmicrokernelcore ;
        \end{axis}
      \end{tikzpicture}
      \begin{tikzpicture}
        \begin{axis}[
            title = Nehalem (HT),
            y tick label style={
            /pgf/number format/.cd,
                fixed,
                fixed zerofill,
                precision=1,
            /tikz/.cd
            },
            width = \textwidth/0.85,
            height = 4.0cm,
            font = \footnotesize,
            domain = 0:4096,
            xtick = {0,1024,...,4096},
            xmin = 0,
            xmax = 4096,
            cycle list name = exotic
          ]
          \addplot[ycomb] table[x expr = \thisrowno{0}*16, y = cycles:u] \tblmicrokernelnehalem ;
        \end{axis}
      \end{tikzpicture}
    \end{column}
    \begin{column}{.50\textwidth}
      \begin{tikzpicture}
        \begin{axis}[
            title = Ivy Bridge,
            y tick label style={
            /pgf/number format/.cd,
                fixed,
                fixed zerofill,
                precision=1,
            /tikz/.cd
            },
            width = \textwidth/0.85,
            height = 4.0cm,
            font = \footnotesize,
            domain = 0:4096,
            xtick = {0,1024,...,4096},
            xmin = 0,
            xmax = 4096,
            cycle list name = exotic
          ]
          \addplot[ycomb] table[x expr = \thisrowno{0}*16, y = cycles:u] \tblmicrokernelivybridge ;
        \end{axis}
      \end{tikzpicture}
    \end{column}
  \end{columns}
\end{frame}
